Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-26 replication_paper/arxiv_draft/paper.tex
can knit!
arXiv submit and readme

\begin{abstract}
How do international crises unfold? We conceptualize of international
relations as a strategic chess game between adversaries and develop a
systematic way to measure pieces, moves, and gambits accurately and
consistently over a hundred years of history. We introduce a new
ontology and dataset of international events called ICBe based on a very
high-quality corpus of narratives from the International Crisis Behavior
(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
precision than existing state of the art datasets and conduct two
detailed case studies of the Cuban Missile Crisis (1962) and
Crimea-Donbas Crisis (2014). We further introduce two new event
visualizations (event icongraphy and crisis maps), an automated
benchmark for measuring event recall using natural language processing
(sythnetic narratives), and an ontology reconstruction task for
objectively measuring event precision. We make the data, replication
material, and visualizations of every historical episode available at a
companion website www.crisisevents.org.
\end{abstract}

@@

For our corpus, \(D\), we select a set of unusually high-quality
historical narratives from the International Crisis Behavior (ICB)
project (\(n=471\))(SI Appendix, Table A1)(33, 34). Their domain is 20th
and 21st-century crises, defined as a change in the type, or an increase
in the intensity, of disruptive interaction with a heightened
probability of military hostilities that destabilizes states'
relationships or challenges the structure of the international system
(3).\footnote{On near crises see (32).} Crises are a significant focus
of detailed single case studies and case comparisons because they
provide an opportunity to examine behaviors in IR short of, or at least
prior to, full conflict (3, 35--42). Case selection was exhaustive based
on a survey of world news archives and region experts, cross-checked
against other databases of war and conflict, and non-English sources
(33, 43). Each narrative was written by consensus by a small number of
scholars, using a uniform coding scheme, with similar specificity (44).
The corpus is unique in IR because it is designed to be used in a
downstream quantitative coding project.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{Brecher M (1999) International studies in the twentieth
century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA}
presidential address. \emph{International Studies Quarterly}
43(2):213--264.}

\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{Reiter D (2015)
\href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We
Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu
Rev Polit Sci} 18(1):481--499.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{Brecher M, Wilkenfeld J (1982)
\href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}.
\emph{World Politics} 34(3):380--417.}

\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The
{International Crisis Behavior Project}.
doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}

\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{Palmer G, et al. (2021)
\href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset},
2011--2014: {Procedures}, coding rules, and description}. \emph{Conflict
Management and Peace Science}:0738894221995743.}

\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts},
1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \&
Littlefield}) Available at:
\url{https://books.google.com?id=_4VTDwAAQBAJ}.}

\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP
(2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic
Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0:
{Logic}, {Characteristics}, and {Comparisons} to {Alternative
Datasets}}. \emph{Journal of Conflict Resolution} 63(3):811--835.}

\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war:
1816-2007} ({CQ Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016)
\href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at
{Interstate Wars}, 1816--2007}. \emph{Journal of Conflict Resolution}
60(5):956--976.}

\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED
Codebook} version 5.0} ({Department of Peace and Conflict Research,
Uppsala University}).}

\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{Pettersson T, Eck K (2018)
\href{https://doi.org/10.1177/0022343318784101}{Organized violence,
1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}

\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010)
Introducing {ACLED}: An armed conflict location and event dataset:
Special data feature. \emph{Journal of peace research} 47(5):651--660.}

\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov
YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The
global sanctions data base}. \emph{European Economic Review}
129:103561.}

\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the
{Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}

\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{Kinne BJ (2020)
\href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation
Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution}
64(4):729--755.}

\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018)
\href{https://doi.org/10.1177/0738894216646978}{The {International
Border Agreements Dataset}}. \emph{Conflict Management and Peace
Science} 35(5):559--576.}

\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{Vabulas F, Snidal D (2021)
\href{https://doi.org/10.1177/0022343320943920}{Cooperation under
autonomy: {Building} and analyzing the {Informal Intergovernmental
Organizations} 2.0 dataset}. \emph{Journal of Peace Research}
58(4):859--869.}

\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017)
\href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates}
of {War Territorial Claims Data}, 1816--20011}. \emph{Journal of Peace
Research} 54(1):99--108.}

\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020)
\href{https://doi.org/10.1177/0022343320929740}{What are the drivers of
diplomacy? {Introducing} and testing new annual dyadic data measuring
diplomatic exchange}. \emph{Journal of Peace
Research}:0022343320929740.}

\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{Sechser TS (2011)
\href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent
Threats}, 1918--2001}. \emph{Conflict Management and Peace Science}
28(4):377--401.}

\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on
{Schema-based Event Extraction} with {Deep Learning}. Available at:
\url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10,
2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{Halterman A (2020) Extracting {Political Events} from
{Text Using Syntax} and {Semantics}.}

\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018)
Phoenix {Real-Time Event Data}. Available at:
\url{http://eventdata.utdallas.edu}.}

\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data.
\emph{Harvard Dataverse} 12.}

\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing
the {UCDP Candidate Events Dataset}. \emph{Research \& Politics}
7(3):2053168020935257.}

\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017)
{OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/}
{[}Accessed September 1, 2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
\CSLLeftMargin{27. }
\CSLRightInline{Zhang H, Pan J (2019)
\href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning
Approach} for {Identifying Collective Action Events} with {Text} and
{Image Data} from {Social Media}}. \emph{Sociological Methodology}
49(1):1--57.}

\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Steinert-Threlkeld ZC (2019)
\href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event
Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
\CSLLeftMargin{29. }
\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis
escalation to war: {Findings} from the {International Crisis Behavior
Project}. \emph{What Do We Know About War}.}

\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
\CSLLeftMargin{30. }
\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and
violence: Twentieth-century findings. \emph{Handbook of war studies
II}:282--300.}

\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
\CSLLeftMargin{31. }
\CSLRightInline{James P (2019)
\href{https://doi.org/10.1177/0738894218793135}{What do we know about
crisis, escalation and war? {A} visual assessment of the {International
Crisis Behavior Project}}. \emph{Conflict Management and Peace Science}
36(1):3--19.}

\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
\CSLLeftMargin{32. }
\CSLRightInline{Iakhnis E, James P (2019)
\href{https://doi.org/10.1177/0738894219855610}{Near crises in world
politics: {A} new dataset}. \emph{Conflict Management and Peace
Science}:0738894219855610.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
(2017) \emph{International {Crisis Behavior Data Codebook}} Available
at: \url{http://sites.duke.edu/icbdata/data-collections/}.}

\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
\CSLLeftMargin{34. }
\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
{Crisis}} ({University of Michigan Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
\CSLLeftMargin{35. }
\CSLRightInline{Holsti OR (1965)
\href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The
American Political Science Review} 59(2):365--378.}

\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
24-30, 1950} ({Free Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
{Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}

\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
nations: {Bargaining} and decision making in international crises}
({Princeton University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{Gavin FJ (2014)
\href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security
Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies}
37(2):319--331.}

\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
foreign policy: {Theory} and practice} ({Columbia University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{Gaddis JL (1987)
\href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}:
{Historians}, {Political Scientists}, and the {Enrichment} of {Security
Studies}}. \emph{International Security} 12(1):3--21.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
\emph{Journal of Conflict Resolution} 32(3):426--456.}

\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
{Asian} security: {Using Europe} to study {Asia}. \emph{Journal of
Global Security Studies} 4(3):393--401.}

>>>>

\begin{abstract}
How do international crises unfold? We conceptualize of international
relations as a strategic chess game between adversaries and develop a
systematic way to measure pieces, moves, and gambits accurately and
consistently over a hundred years of history. We introduce a new
ontology and dataset of international events called ICBe based on a very
high-quality corpus of narratives from the International Crisis Behavior
(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
precision than existing state of the art datasets and conduct two
detailed case studies of the Cuban Missile Crisis (1962) and
Crimea-Donbas Crisis (2014). We further introduce two new event
visualizations (event icongraphy and crisis maps), an automated
benchmark for measuring event recall using natural language processing
(sythnetic narratives), and an ontology reconstruction task for
objectively measuring event precision. We make the data, online
appendix, replication material, and visualizations of every historical
episode available at a companion website www.crisisevents.org and the
github repository.
\end{abstract}

@@

For our corpus, \(D\), we select a set of unusually high-quality
historical narratives from the International Crisis Behavior (ICB)
project (\(n=471\))(SI Appendix, Table A1)(33, 34).\footnote{The Online
  Appendix is at the
  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
  Github Repository}.} Their domain is 20th and 21st-century crises,
defined as a change in the type, or an increase in the intensity, of
disruptive interaction with a heightened probability of military
hostilities that destabilizes states' relationships or challenges the
structure of the international system (3).\footnote{On near crises see
  (32).} Crises are a significant focus of detailed single case studies
and case comparisons because they provide an opportunity to examine
behaviors in IR short of, or at least prior to, full conflict (3,
35--42). Case selection was exhaustive based on a survey of world news
archives and region experts, cross-checked against other databases of
war and conflict, and non-English sources (33, 43). Each narrative was
written by consensus by a small number of scholars, using a uniform
coding scheme, with similar specificity (44). The corpus is unique in IR
because it is designed to be used in a downstream quantitative coding
project.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Brecher M (1999) International studies in the twentieth
century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA}
presidential address. \emph{International Studies Quarterly}
43(2):213--264.}

\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Reiter D (2015)
\href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We
Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu
Rev Polit Sci} 18(1):481--499.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Brecher M, Wilkenfeld J (1982)
\href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}.
\emph{World Politics} 34(3):380--417.}

\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The
{International Crisis Behavior Project}.
doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}

\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Palmer G, et al. (2021)
\href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset},
2011--2014: {Procedures}, coding rules, and description}. \emph{Conflict
Management and Peace Science}:0738894221995743.}

\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts},
1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \&
Littlefield}) Available at:
\url{https://books.google.com?id=_4VTDwAAQBAJ}.}

\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP
(2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic
Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0:
{Logic}, {Characteristics}, and {Comparisons} to {Alternative
Datasets}}. \emph{Journal of Conflict Resolution} 63(3):811--835.}

\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war:
1816-2007} ({CQ Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016)
\href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at
{Interstate Wars}, 1816--2007}. \emph{Journal of Conflict Resolution}
60(5):956--976.}

\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED
Codebook} version 5.0} ({Department of Peace and Conflict Research,
Uppsala University}).}

\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Pettersson T, Eck K (2018)
\href{https://doi.org/10.1177/0022343318784101}{Organized violence,
1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}

\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010)
Introducing {ACLED}: An armed conflict location and event dataset:
Special data feature. \emph{Journal of peace research} 47(5):651--660.}

\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov
YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The
global sanctions data base}. \emph{European Economic Review}
129:103561.}

\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the
{Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}

\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Kinne BJ (2020)
\href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation
Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution}
64(4):729--755.}

\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018)
\href{https://doi.org/10.1177/0738894216646978}{The {International
Border Agreements Dataset}}. \emph{Conflict Management and Peace
Science} 35(5):559--576.}

\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Vabulas F, Snidal D (2021)
\href{https://doi.org/10.1177/0022343320943920}{Cooperation under
autonomy: {Building} and analyzing the {Informal Intergovernmental
Organizations} 2.0 dataset}. \emph{Journal of Peace Research}
58(4):859--869.}

\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017)
\href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates}
of {War Territorial Claims Data}, 1816--20011}. \emph{Journal of Peace
Research} 54(1):99--108.}

\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020)
\href{https://doi.org/10.1177/0022343320929740}{What are the drivers of
diplomacy? {Introducing} and testing new annual dyadic data measuring
diplomatic exchange}. \emph{Journal of Peace
Research}:0022343320929740.}

\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{Sechser TS (2011)
\href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent
Threats}, 1918--2001}. \emph{Conflict Management and Peace Science}
28(4):377--401.}

\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on
{Schema-based Event Extraction} with {Deep Learning}. Available at:
\url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10,
2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Halterman A (2020) Extracting {Political Events} from
{Text Using Syntax} and {Semantics}.}

\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018)
Phoenix {Real-Time Event Data}. Available at:
\url{http://eventdata.utdallas.edu}.}

\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data.
\emph{Harvard Dataverse} 12.}

\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing
the {UCDP Candidate Events Dataset}. \emph{Research \& Politics}
7(3):2053168020935257.}

\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017)
{OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/}
{[}Accessed September 1, 2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Zhang H, Pan J (2019)
\href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning
Approach} for {Identifying Collective Action Events} with {Text} and
{Image Data} from {Social Media}}. \emph{Sociological Methodology}
49(1):1--57.}

\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Steinert-Threlkeld ZC (2019)
\href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event
Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis
escalation to war: {Findings} from the {International Crisis Behavior
Project}. \emph{What Do We Know About War}.}

\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and
violence: Twentieth-century findings. \emph{Handbook of war studies
II}:282--300.}

\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{James P (2019)
\href{https://doi.org/10.1177/0738894218793135}{What do we know about
crisis, escalation and war? {A} visual assessment of the {International
Crisis Behavior Project}}. \emph{Conflict Management and Peace Science}
36(1):3--19.}

\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Iakhnis E, James P (2019)
\href{https://doi.org/10.1177/0738894219855610}{Near crises in world
politics: {A} new dataset}. \emph{Conflict Management and Peace
Science}:0738894219855610.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
(2017) \emph{International {Crisis Behavior Data Codebook}} Available
at: \url{http://sites.duke.edu/icbdata/data-collections/}.}

\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
{Crisis}} ({University of Michigan Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Holsti OR (1965)
\href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The
American Political Science Review} 59(2):365--378.}

\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
24-30, 1950} ({Free Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
{Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}

\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
nations: {Bargaining} and decision making in international crises}
({Princeton University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Gavin FJ (2014)
\href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security
Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies}
37(2):319--331.}

\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
foreign policy: {Theory} and practice} ({Columbia University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Gaddis JL (1987)
\href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}:
{Historians}, {Political Scientists}, and the {Enrichment} of {Security
Studies}}. \emph{International Security} 12(1):3--21.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
\emph{Journal of Conflict Resolution} 32(3):426--456.}

\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
{Asian} security: {Using Europe} to study {Asia}. \emph{Journal of
Global Security Studies} 4(3):393--401.}

\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Hewitt JJ (2001)
\href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International
Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to
{Teach Conflict} and {Crisis Analysis}}. \emph{Int Stud Perspect}
2(4):371--383.}
